### 2023-08-16 paper/sec-dis-pseudodata.tex
sect 2

Structure functions depend only on $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
for the neutrino scattering through the nuclear modifications of the proton PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
\ee
and in addition here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that
 structure functions are decomposed as
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
%
in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
Specifically, in this work we impose that $Q^2\ge 2$ GeV$^2$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
 %
We discuss in Sect.~\ref{sec:settings} the theoretical
settings adopted~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
evaluate predictions for
neutrino DIS structure functions
and differential cross-sections,
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}),~(\ref{eq:antineutrino_DIS_xsec_FL}), and~(\ref{eq:sfs_pqcd}),
in the kinematics covered by LHC neutrinos.

@@

 In the projections presented in this work, when interpreting the LHC neutrino structure
 functions in terms of proton PDFs, we will assume a isoscalar free-nucleon target and neglect
 nuclear PDF modifications, along the lines of Eq.~(\ref{eq:neutrinoSFs_isoscalar}).
 %
 On the other hand, when evaluating structure functions
 for a tungsten (W) target, we keep into account both
 nuclear corrections and that
 the target is not isoscalar when evaluating the physical observables.
 %
 We point out that accounting for nuclear modifications in a global proton
 PDF fit is possible by means of the procedure developed
 in~\cite{Ball:2020xqw,Ball:2018twp}.

 It is illustrative to compare the PDF dependence of neutrino structure functions
 at LO with that of their counterparts for neutral-current
 scattering with a charged lepton projectile.
 %
 Within the same assumptions, for energies below
 the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
 partonic decomposition is
 the 
 \bea
 F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
 F_2^{\ell n}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, ,\label{eq:NC_chargedlepton}   \\
 F_2^{\ell N}(x,Q^2) &=& x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
 + \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \nonumber  
 \eea
 with $xF_3$ being negligible in this region below the $Z$-pole.
 %
 Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
 neutrino and charged-lepton DIS in terms of sensitivity
 to the different flavour PDF decomposition.

 \subsection{Far-forward neutrino detectors at the LHC}
 \label{sec:neutrinoDetectors}

 The calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors involves two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 Here we summarise the main features of each of the existing and future
 far-forward detectors considered, in particular concerning
 their acceptance and performance.
 %
 We focus on  muon neutrino scattering, which benefits from the highest rates and is less
 affected by theoretical uncertainties in the production mechanism.

 The kinematics of a charged-current neutrino DIS event $(x,Q^2, E_\nu)$,
 or alternatively $(x,Q^2, y)$, are uniquely specified by the measurement of three independent
 final-state variables,
 such as $\lp E_\ell,\theta_\ell, W^2\rp$ or $\lp E_\ell,\theta_\ell, E_h \rp$,
 with $E_\ell$ and $\theta_\ell$ being the energy and polar angle of the outgoing
 charged lepton and $E_h$ the total energy of the hadronic final state.
 %
 Most neutrino detectors can only access $E_h$, given that $W^2$ requires
 fully reconstructing this final state.
 %
 A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixes the DIS kinematics as:
 \bea
 E_\nu &=& E_h + E_\ell \, , \nonumber \\
 Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,  \label{eq:dis_kinematic_mapping}\\
 x&=& \frac{4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp}{2m_N E_h} \, .\nonumber
 \eea
 These relations also indicate how systematic uncertainties affecting the measurement
 of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
 reconstructed values of  $(x,Q^2, E_\nu)$ modifying the expected
 binned event rates.

 Table~\ref{tab:FPF_experiments} summarises,
 for each of the far-forward LHC neutrino experiments considered,
 their pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos.
  %
  For these projections we assume that FASER$\nu$ and SND@LHC acquire data
  for Run III ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2,
  AdvSND, and FLArE take data
  for the complete HL-LHC period  ($\mathcal{L}=3$ ab$^{-1}$).
  %
  In the following we provide more details about the information collected in
  Table~\ref{tab:FPF_experiments}.

@@

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the begin of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 meters from the ATLAS interaction point and has been taking data
since the  beginning of Run 3.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume of 830 kg, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

\paragraph{FASER$\nu$2.}
%
A proposed 20-ton neutrino experiment located on the LOS
of the LHC neutrino beam to be installed in the FPF cavern.
%
It is based on the same technology as FASER$\nu$, and hence
relies on a emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
It would be sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS) and a near detector installed somewhere else in LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
 In the following we focus on the AdvSND-far detector.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment relies on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
 %
 FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
 while  fully containing the events as required for kinematic reconstruction.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 While muon neutrinos with energy $E_\nu \gsim 2$ GeV would not be fully
 contained in the  FLArE detector,
for the projections presented in this work
 we assume that outgoing muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.
 %
 With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$5\% of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since muon neutrinos would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
 to be the same as those of FASER$\nu$2.

\subsection{Differential event rate calculation}
\label{sec:pseudo-data_generation}

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
The goal is to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
When choosing the binning of the measurement, the main criteria are
simplicity and ensuring that Gaussian statistics holds in all bins.

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are therefore evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.

@@

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
considered, separated into electron neutrinos and antineutrinos
and muon neutrinos and antineutrinos.
%
As mentioned above, for FLArE we assume that muon neutrinos interacting
in its fiducial volume will be measured
by the FASER$\nu$2 spectrometer.
  %
These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the only
requirement that the momentum transfer and the final-state invariant mass are restricted
to the DIS region,
\be
\label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
\ee
%
The numbers in parenthesis indicate the event rates corresponding to charm
production, for those experiments with heavy flavour tagging capabilities.
%
We note that, as opposed to the number of interacting neutrinos
computed in~\cite{Feng:2022inv}, we now account for the 
detector acceptance listed in  Table~\ref{tab:FPF_experiments}.

>>>>

Structure functions depend only on $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
for the neutrino scattering through the nuclear modifications of the free-nucleon PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
\ee
and in addition here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that
 structure functions can be decomposed as
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
%
in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
 %
We discuss below the theoretical
settings adopted here~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
evaluate predictions for
neutrino differential cross-sections and DIS structure functions,
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}),~(\ref{eq:antineutrino_DIS_xsec_FL}), and~(\ref{eq:sfs_pqcd}),
in the kinematics covered by LHC neutrinos.

@@

 In the projections presented in this work, when interpreting the LHC neutrino structure
 functions in terms of proton PDFs, we will assume a isoscalar free-nucleon target and neglect
 nuclear PDF modifications, along the lines of Eq.~(\ref{eq:neutrinoSFs_isoscalar}).
 %
 On the other hand, when evaluating structure functions
 for a tungsten (W) target, we keep into account both
 nuclear corrections and that
 the target is not isoscalar when evaluating the physical observables.
 %
 Accounting for nuclear modifications in a global proton
 PDF fit is possible by means of the procedure developed
 in~\cite{Ball:2020xqw,Ball:2018twp} based on
 the theory covariance matrix approach~\cite{NNPDF:2019vjt,NNPDF:2019ubu}.

 It is illustrative to compare the PDF dependence of neutrino structure functions
 at LO with that of their counterparts for neutral-current
 scattering with a charged lepton projectile.
 %
 Within the same assumptions, for energies below
 the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
 partonic decomposition is
 the 
 \bea
 F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
 F_2^{\ell n}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, ,\label{eq:NC_chargedlepton}   \\
 F_2^{\ell N}(x,Q^2) &=& x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
 + \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \nonumber  
 \eea
 with $xF_3$ being negligible in this region below the $Z$-pole.
 %
 Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
 neutrino and charged-lepton DIS in terms of sensitivity
 to the different flavour PDF decomposition.
 %
 This implies that the best sensitivity on the quark
  flavour separation in the nucleon
 would be provided by combining neutrino DIS at
 LHC far-forward experiments with measurements on charged-lepton
 DIS at the EIC.

 \subsection{LHC far-forward neutrino detectors}
 \label{sec:neutrinoDetectors}

 The calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors involves two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 Here we summarise the main features of each of the existing and future
 far-forward detectors considered, in particular concerning
 their acceptance and (expected) performance.
 %
 We focus on  muon neutrino scattering, which benefits from the highest rates and is less
 affected by theoretical uncertainties in the production mechanism.

 The kinematics of a charged-current neutrino DIS event $(x,Q^2, E_\nu)$,
 or alternatively $(x,Q^2, y)$, are uniquely specified by the measurement of three independent
 final-state variables,
 such as $\lp E_\ell,\theta_\ell, W^2\rp$ or $\lp E_\ell,\theta_\ell, E_h \rp$,
 with $E_\ell$ and $\theta_\ell$ being the energy and polar angle of the outgoing
 charged lepton and $E_h$ the total energy of the hadronic final state.
 %
 Most neutrino detectors can only access $E_h$, given that $W^2$ requires
 fully reconstructing this final state.
 %
 A measurement of the three kinematic variables $\lp E_\ell,\theta_\ell, E_h \rp$ then fixes the DIS kinematics as:
 \bea
 E_\nu &=& E_h + E_\ell \, , \nonumber \\
 Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,  \label{eq:dis_kinematic_mapping}\\
 x&=& \frac{4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp}{2m_N E_h} \, .\nonumber
 \eea
 These relations also indicate how systematic uncertainties affecting the measurement
 of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
 reconstructed values of  $(x,Q^2, E_\nu)$ modifying the expected
 binned event rates.

 Table~\ref{tab:FPF_experiments} summarises,
 for each of the far-forward LHC neutrino experiments considered in this
 work,
 their pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos.
  %
  For these projections we assume that FASER$\nu$ and SND@LHC acquire data
  for Run III ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2,
  AdvSND, and FLArE take data
  for the complete HL-LHC period  ($\mathcal{L}=3$ ab$^{-1}$).
  %
   In the case of FLArE, we consider projections for both
  for 10 ton and 100 fiducial volume detectors.
  %
  In the following we provide more details about the information collected in
  Table~\ref{tab:FPF_experiments}.

@@

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 meters from the ATLAS interaction point and has been taking data
since the  beginning of Run III.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume of 830 kg, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

\paragraph{FASER$\nu$2.}
%
A proposed 20-ton neutrino experiment located on the LOS
of the LHC neutrino beam to be installed in the FPF cavern.
%
It is based on the same technology as FASER$\nu$, and hence
relies on a emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
It would be sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.
%
Given that FASER$\nu$2 is based on the same detector technology
as its predecessor, the same performance in terms of reconstruction
of final-state kinematics is assumed.

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
 In the following we focus on the AdvSND-far detector.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.
 %
 No information on the expected performance of the AdvSND-far detector
 is available and hence to estimate of the systematic errors
 is carried out.

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment
 would rely on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
 %
 FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
 while containing the events as required for kinematic reconstruction.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 While muon neutrinos with energy $E_\nu \gsim 2$ GeV would not be fully
 contained in the  FLArE detector,
for the projections presented in this work
we assume that outgoing high-energy
muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.

 With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  while final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
 downstream in the FPF cavern.
 %
 We consider projections both for 10 ton (FLArE-10) and 100 ton (FLArE-100) fiducial volume detectors.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$5\% of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since muon neutrinos would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
 to be the same as those of FASER$\nu$2 as indicated
 in Table~\ref{tab:FPF_experiments}.

\subsection{Differential scattering event rates}
\label{sec:pseudo-data_generation}

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
We want to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
When choosing the binning of the measurement, the main criteria are
simplicity and ensuring that Gaussian statistics holds in all bins.

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Differential event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptance thresholds
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.

@@
